Size-differentiated Export in Different Dynamical Regimes in the Ocean

### 2020-03-15 Submission_and_reviews/response_to_reviewers.tex

%_____________________________________________
\begin{document}

% Article title and author
\begin{center}
\large
\textbf{
Response to reviewers\\}
\end{center}
\small

\section{Response to Editor's comments}

Comments provided by reviewer \#1 are constructive and relevant. They lead to major changes in the manuscript, namely figure 7 and 8. It also led us to clarify some of the aspects of the manuscript, as the scientific reasoning behind some of the choices made (e.g., particle seeding depth). Most of the concerns rose by the reviewer were, however, related to the definition of an export horizon to quantify export. We argue, based on both our work and recent studies \citep{Palevsky_2018}, that the definition of an export horizon is not adequate and introduces subjectivity and biases in the results.

@@

Finally, the small particles released at the base of the euphotic layer do not aim to represent small particles at the time of particle production. It can also represent larger particles at production that went through remineralization in the ML.

Based on this comment, the text has been modified in Section 2.2.2 to better justify the choices outlined above.\\

\subsection*{Major point \#2}
\textit{Second, it is unclear why 5m/day is selected for the largest particle class. Studies using Underwater Vision Profilers reveal that a large portion of the particle flux is contributed by large aggregates of 0.1-5mm, which can have sinking speeds above 100m/day (see Guidi et al. 2008, Kiko et al. 2017). Comparing the summer and winter simulations, it seems that small particles only dominate the export flux when vertical advective velocities exceed the large particle sinking velocity. This condition would not be met if an aggregate particle class with sinking velocity of 100m/day were included. I suggest the inclusion of an additional "large aggregate" size class with appropriate sinking speed.\\}

\textit{``it is unclear why 5m/day is selected for the largest particle class."\\}
The choice of 5m/day sinking rates as the ``fast-sinking"  class is justified on lines 300-301 of the original manuscript. It is based on the PDFs of the advective vertical velocity. In our case, 5 m/day is faster than 85-90\% of the vertical velocity modeled in our domain at any given time. We have added some text in Section 2.2.2 to make the justification clearer to the reader.\\

@@

\textit{For particles released at 80m, sinking at 5m/day and remineralizing at a rate of 0.13/day, it seems that at least 50\% of the inital biomass in the large size category must be exported through the 100m horizon, before remineralizing. In contrast, Figure 6 shows that only a very small fraction of the small particles reach 100m in winter, even when they are not remineralizing. It therefore seems that even in winter, large particles must dominate the integrated export flux in the simulation with remineralization, contradicting the second major conclusion of the study.\\}

This is a good example of how defining an arbitrary export horizon can skew the results. If the export horizon was set to 90 m, then almost all of the 1m/day particles would be "exported", and they would therefore dominate export for $\xi=4$. If 100 m is used as an export horizon, this is no longer the case and the 5m/day class would dominate export. if 300 m was used, then there would be no export. A large flux of biomass, even over a limited vertical scale, has the potential to lead to a large export. This is why we focus on biomass fluxes as opposed to integrated biomass. Along with other reasons mentioned above (seeding strategy, operational limitations, etc).\\

\textit{I suggest the authors repeat their analysis, comparing time-integrated export through 100m in order to assess the contribution of large vs. small particles.\\}

This was the original direction that we took for this study. However, we came to realize that looking at time-integrated export introduces large complications, the main ones being: (1) It requires defining an export depth, and (2) The one-time particle seeding strategy becomes inappropriate. Constant reseeding becomes necessary, which is operationally constraining, (3) the timescales integrated over drives the result. If particles are tracked for an infinitely long time, they will eventually all be exported, and the dominant particle class is only a function of the Junge slope. If particles are tracked for long enough for one class to cross the export horizon, but not other classes (as it would be the case for a horizon defined a t100 m), then the export would artificially be driven by the fast sinking particles.

@@

\subsection*{Minor comments}
\textit{Line 306: Is it three weeks, or 28 days (four weeks)?}\\
\rep{Text has been modified accordingly.}
\textit{Figure 7+8: It would be useful to point out either in the caption or axis label that the x axes are the vertical velocity combining both sinking and advective components, and that the velocity in the legends is the initial sinking velocity. This confused me for a few minutes.}\\
\rep{Figure captions have been modified.}
\textit{Acknowledgments: Will the model output be archived for public access?}\\
\rep{Due to the very large amount of data necessary for this study, a subset of the data, equired to produce the figures, is publicly available (link is now included in acknowledgments). Full dataset is available on request.}

\section{Comments from Reviewer  \#2}
\rep{We would first like to thank this Reviewer for these very on-point and constructive reviews. They were very helpful to make the manuscript stronger!}

\section*{Range of sinking speeds.}
\textit{The sinking speed examined by the authors are 0.025, 0.05, 1 and 5 m/d. All these values would be considered as "slow sinking rate" by the community. Yet, the manuscript concludes on the relative contribution of slow and fast sinking particles, which is misleading. It also means that the authors cannot really conclude about the relative role of particles that have sinking rates similar in magnitude or faster than submesoscale motions (i.e. 50-300 m/d).\\}

The three sinking rates were defined based on having one class virtually non-sinking (0.025 m/day), one class within the range of $w$ modeled (1 m/day), and one class larger than $w$ modeled at submesoscale in the winter case (5 m/day). In fact, at any given time, at least 85\% of the modeled vertical velocity is smaller than 5 m/day -- our fastest sinking rate -- and an even larger percentage is sampled by the Lagrangian particles. For all intents and purposes, a 5 m/day sinking particle is ``fast" compared to the dynamical flow of the simulations. Any particle class with a faster sinking rate would behave in a predictable way, as vertical velocity is dominated by sinking. We modified the text in Section 2.2.2 to clarify this (Line 304 - 307)

, which is the 90percentile of the PDF for $w$ showed in Fig 5). Selecting a sinking rate much faster than that would bring us back to the traditional 1D model, as the sinking rate would greatly dominate the vertical flux. The objective of the study is to capture that transitional part of the size spectrum. Station Papa remains a relatively calm region, so submesoscale $w$ are of the order of 50 m/day. Other regions with stronger vorticity would have $w$ of the order of magnitude you suggest ($\sim$ 100 m/day) and would affect a greater part of the particle size spectrum.

### 2020-03-15 size_differentiated_export.tex
update revised manuscript
Not final version

% Trackchanges package
\usepackage{trackchanges}
\soulregister\ref7 % For references and citation to work within trackchanges
\soulregister\cite7
%% PLEASE USE THE FOLLOWING COMMANDS
%   \note[editor]{The note} 
%   \annote[editor]{Text to annotate}{The note} 
%   \add[editor]{Text to add} 
%   \remove[editor]{Text to remove} 
%   \change[editor]{Text to remove}{Text to add}

@@

	%FIG8
	\begin{figure}[t!]
		\centering
		\includegraphics[width = 1\linewidth]{Fig8_revised.png}
		\caption{\change{Probability Distribution Function (PDF) of relative biomass versus total vertical velocity along particle trajectories in the summer case [left] and winter case [right], ignoring [top] and including [bottom] particle remineralization, for $\xi$ = 4 and 25 days after particle release. Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class, categorized according to their initial sinking velocity. Remineralization processes have the greatest impact on fast-sinking particles, especially in summer dynamics.}{Same as Figure \ref{fig: biomass_export}, but including particle remineralization (see Equation \ref{eq: sinking_velocity_remin}).}
		}	
		\label{fig: biomass_export_remin}
	\end{figure}
	In a advectively-driven system where $\left<w_sB\right> \sim \left<wB\right>$, the relative amount of biomass content in a particle class becomes important and dictates the respective contribution of each particle class to the total downward biomass fluxes. This shift from a gravitationally-driven to an advectively-driven system is observed when implementing particle remineralization in the summer (Figure \ref{fig: biomass_export_remin}\remove{c}): in the absence of remineralization, faster-sinking particles dominate the downward biomass fluxes (\change{60}{53}\%; see Figure \ref{fig: biomass_export}c). When remineralization processes are considered, slower-sinking particles \change{become the dominant contributor}{contribute more} to biomass fluxes (see inset in Figure \ref{fig: biomass_export_remin}c). As shown in Figure \ref{fig: biomass_export}, downward biomass fluxes in the wintertime are generally advectively-driven, due to the larger vertical velocities associated with wintertime ocean dynamics. Biomass fluxes are dominated by the slower-sinking particles \add{when $\xi =4$}, representing 79\% of the downward biomass flux (Figure \ref{fig: biomass_export}d). Even after implementing the remineralization scheme, slower-sinking particles remain the largest contributor to downward biomass fluxes (82\%; see Figure \ref{fig: biomass_export_remin}d).

>>>>

% Trackchanges package
\usepackage{trackchanges}
\soulregister\ref7
\soulregister\cite7
%% PLEASE USE THE FOLLOWING COMMANDS
%   \note[editor]{The note} 
%   \annote[editor]{Text to annotate}{The note} 
%   \add[editor]{Text to add} 
%   \remove[editor]{Text to remove} 
%   \change[editor]{Text to remove}{Text to add}

@@

	%FIG8
	\begin{figure}[t!]
		\centering
		\includegraphics[width = 1\linewidth]{Fig8_revised.png}
		\caption{\change{Probability Distribution Function (PDF) of relative biomass versus total vertical velocity along particle trajectories in the summer case [left] and winter case [right], ignoring [top] and including [bottom] particle remineralization, for $\xi$ = 4 and 25 days after particle release. Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class, categorized according to their initial sinking velocity. Remineralization processes have the greatest impact on fast-sinking particles, especially in summer dynamics.}{Same as Figure \ref{fig: biomass_export}, but including particle remineralization (see Equation \ref{eq: sinking_velocity_remin}).}}	
		\label{fig: biomass_export_remin}
	\end{figure}
	In a advectively-driven system where $\left<w_sB\right> \sim \left<wB\right>$, the relative amount of biomass content in a particle class becomes important and dictates the respective contribution of each particle class to the total downward biomass fluxes. This shift from a gravitationally-driven to an advectively-driven system is observed when implementing particle remineralization in the summer (Figure \ref{fig: biomass_export_remin}\remove{c}): in the absence of remineralization, faster-sinking particles dominate the downward biomass fluxes (\change{60}{53}\%; see Figure \ref{fig: biomass_export}c). When remineralization processes are considered, slower-sinking particles \change{become the dominant contributor}{contribute more} to biomass fluxes (see inset in Figure \ref{fig: biomass_export_remin}c). As shown in Figure \ref{fig: biomass_export}, downward biomass fluxes in the wintertime are generally advectively-driven, due to the larger vertical velocities associated with wintertime ocean dynamics. Biomass fluxes are dominated by the slower-sinking particles \add{when $\xi =4$}, representing 79\% of the downward biomass flux (Figure \ref{fig: biomass_export}d). Even after implementing the remineralization scheme, slower-sinking particles remain the largest contributor to downward biomass fluxes (82\%; see Figure \ref{fig: biomass_export_remin}d).
